Placeholder Title... Something About Delegating Quantum Computations

### 2019-10-15 longoutput.tex
Add reference on de Finetti
Write a bit on de Finetti

In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial. As seen in \cite{kitaev2002classical}, the prover, honest or not, cannot do better than sending $n$ identical copies of some state. As a result, a simple Chernoff bound would suffice. The same reasoning does not generalize trivially to our case, so instead we give the following proof.

@@

>>>>

In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial. As seen in \cite{kitaev2002classical}, a prover, honest or not, cannot do better than sending $n$ identical copies of some state. As a result, a simple Chernoff bound would suffice. The same reasoning does not generalize to our case, so instead we give the following proof.

@@

Now we consider the general case. We use \autoref{deFinetti}. Let $n=l$ and $N=k=\poly(l)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily small. That is, with some arbitrarily small error in measurement results, we can assume without the loss of generality that the client receives an input of the simple form above. Hence concludes the proof.

### 2019-10-15 preliminaries.tex
Do more work on longoutput
Use projection lemma
Write a bit on de Finetti

Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.

Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
Then $\exists J\in\mathbb{R}$ s.t.
$\lambda(H_1\big|_S)-\frac{1}{8}\leq
	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.

>>>>

Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.
\begin{theorem}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$.
	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda(H_2|_{K^\bot})}$$
	$$\lambda(H_1+JH_2)\geq\lambda(H_1\big|_K)-\frac{1}{8}$$
\end{theorem}

\subsection{Quantum de Finetti Theorem under Local Measurements}

Here is a theorem taken from \cite{Brandão2017}.
\begin{theorem}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there is a measure $\nu$ on $D(A)$ such that
	$$\max_{\Lambda_2,\ldots,\Lambda_l\in\mathcal{M}}\norm{(id\otimes\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\int \nu(d\sigma)\sigma^{\otimes l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
\end{theorem}
